Paper Figure Generation

### 2022-07-11 R/PaperFigureGeneration.rmd
Third generation of figure plots
- Updated plotting notebook
- Added parameters to plotting functions where necessary, such as axis labels or limits.
- Added TG-filtering option in NHF1 notebooks.

```{r read_figure_2_data}
NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllReps)) {
  NHF1CPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMismatchDataAllReps)[i]
  ))
}
```

```{r figure_2A}
plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`,
                            title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")
```
```{r figure_2B}
plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context")
```
```{r figure_2C}
plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies")
```
```{r figure_2D}
plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies")
```

```{r read_figure_3_data}
NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllReps)) {
  NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMMFreqZScoresAllReps)[i], includedMismatches = c("C>T")
  ))
}

@@

```{r figure_3A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
```
```{r figure_3B, fig.width = 6, fig.height = 5}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_3C, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
                        expansionOffset = 10, minReadLength = 21, maxReadLength = 27)

### All timepoints together ###
# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
#                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27)
```

```{r read_figure_5_data}
NHF1CPDMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllRepsFiltered)) {
  NHF1CPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

@@

NHF1CPDMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsFiltered)) {
  NHF1CPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(NHF1CPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

@@

```{r figure_5A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
```
```{r figure_5B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME)
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME)
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME)
```
```{r figure_5C}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

@@

```{r read_figure_6_data}
NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
))

NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))

NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

```

```{r figure_6A, fig.width = 6, fig.height = 5}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_6B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
```
```{r figure_6C, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
```

```{r read_figure_7_data}
# Note: This file was created manually by combining/modifying a couple different files counting tandem mismatches.
NHF1TandemMismatchCountsComparisonAllReps = fread(generateFilePath(
  NHF1MismatchesByReadDataDirectory, dataTypeStrings$tandemMismatchCountsComparison, ".tsv",
  cellType = "NHF1", repitition = "all_reps"
))
```

```{r figure_7B, fig.width = 8, fig.height = 5}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD" & Timepoint == "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25) +
      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1")
  )
```

>>>>

```{r read_figure_1_data}
NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllReps)) {
  NHF1CPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMismatchDataAllReps)[i]
  ))
}
```

```{r figure_1B}
plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`, ylim = c(0,0.8),
                            title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")
```
```{r figure_1C}
plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context")
```
```{r figure_1D}
plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies")
```

```{r read_figure_2_data}
NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllReps)) {
  NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMMFreqZScoresAllReps)[i], includedMismatches = c("C>T")
  ))
}

@@

```{r figure_2A, fig.width = 5, fig.height = 6}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         yAxisLabel = "Relative C>T Frequency",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          yAxisLabel = "Relative C>T Frequency",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
```
```{r figure_2B, fig.width = 6.5, fig.height = 6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
                               xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 8,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_2C, fig.width = 5, fig.height = 6}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
                        expansionOffset = 10, minReadLength = 20, maxReadLength = 27,
                        yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")

### All timepoints together ###
# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
#                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27,
#                         yAxisLabel = "TGG Trinucleotide Frequency", defaultColor = "Black")
```

```{r read_figure_3_data}
NHF1CPDMismatchDataAllRepsTGGFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllRepsTGGFiltered)) {
  NHF1CPDMismatchDataAllRepsTGGFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsTGGFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

@@

NHF1CPDMMFreqZScoresAllRepsTGGFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)) {
  NHF1CPDMMFreqZScoresAllRepsTGGFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(NHF1CPDMMFreqZScoresAllRepsTGGFiltered)[i], includedMismatches = c("C>T")
  ))
}

@@

```{r figure_3A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
                                         yAxisLabel = "Relative C>T Frequency")
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative C>T Frequency")
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative C>T Frequency")

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
```
```{r figure_3B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["ZT2"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["20min"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 20min All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsTGGFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsTGGFiltered,
#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME, yAxisLabel = "Relative C>T Frequency")
```
```{r figure_3C, fig.width = 7.5, fig.height = 5}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

@@

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))

NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}
```

```{r figure_4A, fig.width = 5, fig.height = 6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
                               xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25,
#                                xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
                        endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```

```{r read_figure_5_data}
# Note: This file was created manually by combining/modifying a couple different files counting tandem mismatches.
NHF1TandemMismatchCountsComparisonAllReps = fread(generateFilePath(
  NHF1MismatchesByReadDataDirectory, dataTypeStrings$tandemMismatchCountsComparison, ".tsv",
  cellType = "NHF1", repitition = "all_reps"
))
```

```{r figure_5B, fig.width = 8, fig.height = 5}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD" & Timepoint == "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(Mismatch_Type, Tandem_Mismatches_Count, fill = Search_Method)) +
      geom_bar(stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD 1h All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      geom_text(aes(label=Tandem_Mismatches_Count), position = position_dodge(width = 0.9), vjust = -0.25, size = 5) +
      blankBackground + defaultTextScaling + scale_fill_brewer(palette = "Set1") + coord_cartesian(ylim = c(0,200000))
  )
```

```{r read_figure_6_data}
NHF1CPDCCtoTTMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)) {
  NHF1CPDCCtoTTMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "CC>TT",
    timepoint = names(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)[i]
  ))
}
